### 2021-01-28 paper.tex
Formal Specification

>>>>

\subsubsection{Security-Related Data Dependencies}
Building the basic formula can be made easy to security experts and to developers as
well, through the patterns that we provide and the rich dictionary for the labels and
the security guidelines that can be used. Writing the MCL formulas does not require
an advanced level in formal methods, or to master the idioms of the language, as we
have shown in the previous section.
